### 2020-05-12 writeup/proof_transfer_ex.tex
A & A.1

We first state several helper lemmas that can be viewed as corollaries of Theorem \ref{thm_model_shift}.
\begin{lemma}\label{lem_minv}[\todo{ref?}]
	Let $X\in\real^{n\times p}$ that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma$.
	In the setting when $n = c p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X^{\top}X)^{-1}\Sigma} = \frac{1}{c - 1}. \]
\end{lemma}

\begin{lemma}\label{lem_cov_shift}
	\todo{restate the setting} In the setting of Theorem \ref{thm_model_shift}, we have with high probability $1-{\rm o}(1)$,
\begin{align}\label{lem_cov_shift_eq}
\tr ((X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2) = \frac{1}{n_1+n_2}\cdot \bigtr{ (a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
\end{align}
	for any constant $\epsilon>0$.
\end{lemma}
We will give the proof of Lemma \ref{lem_cov_shift} in Section \ref{sec_maintools}.

\subsection{Proof of Proposition \ref{prop_transition}}

Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows
The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{v}$ is close to $1$.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
\end{itemize}

>>>>

We state several helper lemmas to get a bound on the variance of $\hat{\beta}_t^{\STL}$ and $\hat{\beta}_t^{\MTL}$.
The first lemma, which is a folklore result in random matrix theory, helps determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p$ goes to infinity.
\begin{lemma}\label{lem_minv}[\todo{ref?}]
	Let $X\in\real^{n\times p}$ that contains i.i.d. row vectors with mean $0$ and covariance $\Sigma$.
	In the setting when $n = c p$ we have that as $p$ goes to infinity,
	\[ \bigtr{(X^{\top}X)^{-1}\Sigma} = \frac{1}{c - 1}. \]
\end{lemma}

The second lemma is a corollary of Theorem \ref{thm_model_shift}.
\begin{lemma}\label{lem_cov_shift}
	Let $X_i\in\real^{n_i\times p}$ be a random matrix that contains i.i.d. row vectors with mean $0$ and variance $\Sigma_i$, for $i = 1, 2$.
	Denote by $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ and let $\lambda_1, \lambda_2, \dots, \lambda_p$ be the singular values of $M^{\top}M$ in decreasing order.
	When $n_1 = c_1 p$ and $n_2 = c_2 p$, we have that with high probability over the randomness of $X_1$ and $X_2$, the following equation holds
	\begin{align}%\label{lem_cov_shift_eq}
		\bigtr{(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{1}{c_1+c_2}\cdot \bigtr{ \frac{1}{p}\cdot(a_1 M^\top M + a_2)^{-1}} +\bigo{ n^{-1/2+\epsilon}},
	\end{align}
	for any constant $\epsilon>0$, where $a_1, a_2$ are solutions to the following deterministic equations:
	\begin{align}
		a_1 + a_2 = 1- \frac{1}{c_1 + c_2},~ a_1 + \sum_{i=1}^p \frac{a_1}{(c_1 + c_2)(a_1 + a_2/ \lambda_i^2)} = \frac{c_1}{c_1 + c_2}. \label{eq_a12}
	\end{align}
\end{lemma}
We will give the proof of Lemma \ref{lem_cov_shift} in Section \ref{sec_maintools}.

\subsection{Proof of Proposition \ref{prop_dist_transition}}

Using Lemma \ref{lem_minv} and \ref{lem_cov_shift}, we can track the change of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as follows

The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{v}$ is close to $1$.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ to show the result.
\end{itemize}

\begin{lemma}
	In the setting of Proposition \ref{prop_dist_transition}, we have that $\abs{\hat{v} = \hat{w_1} / \hat{w_2} - 1} \le o(1)$.
\end{lemma}

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, upper bound]
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}, lower bound]
\end{proof}

### 2020-05-12 writeup/transfer.tex
A & A.1

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_transition}
	In the example described above, we have the following deterministic conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac{2(2c-1)^2}{(c-1)(2c+1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{2(2c-1)^2}{(c-1)(2c+1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

We obtain the following insight from Proposition \ref{prop_transition}.
First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
On the other hand, model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
Hence, the type of transfer is determined by the trade-off between the bias caused by model shift and the reduction of variance.

>>>>

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac{2(2c-1)^2}{(c-1)(2c+1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac{2(2c-1)^2}{(c-1)(2c+1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

We obtain the following insight from Proposition \ref{prop_dist_transition}.
First, adding the source task has the effect of reducing the variance of the estimator, independent of the model shift.
On the other hand, model shift introduces an additional bias term, which scales with $d^2$, the distance of the two task models.
Hence, the type of transfer is determined by the trade-off between the bias caused by model shift and the reduction of variance.
